Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-10 paper.tex
Typo in Redundancy of Backend Services
Typos in Conclusion

	      It is not a necessary condition for DaaS systems in general,

@@

\section{Conclusion and Outlook}
\label{sec:Conclusions}

@@

For future work,
we plan to replace our temporary solution for internal communication
with a more efficient approach as our preliminary performance tests revealed
a potential bottlenack in that particular area.
We also plan to apply certain optimization strategies
with respect to backend and instance communication.
We further plan to enhance our yet limited performance testing
and will provide a full-fledged performance analysis
of realsitic deployment scnarios and utilization patterns
which include an evaluation of different user behaviors
within various popular applications.

>>>>

	      is not a necessary condition for DaaS systems in general,

@@

\section{Conclusion and Outlook}\label{sec:Conclusions}

@@

For future work,
we plan to replace our temporary solution for internal communication
with a more efficient approach as our preliminary performance tests revealed
a potential bottlenack in that particular area.
We also plan to apply certain optimization strategies
with respect to backend and instance communication.
We further plan to enhance our yet limited performance testing
and will provide a full-fledged performance analysis
of realistic deployment scenarios and utilization patterns
which include an evaluation of different user behaviors
within various popular applications.
